Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-29 datapaper_baseline.tex
performance

\subsection{Multi-leaf segmentation and tracking framework}
We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
To generate the template set, we first select $10$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $12$ different sizes in order to cover the entire range of leaf sizes in the database.
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates.

@@

%We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\cite{barrow1977parametric}.
Our work is motivated by Chamfer Matching technique~\cite{barrow1977parametric}, which is used to align two edge maps.
We extend it to simultaneously align multiple overlapping objects.
For each image, we use simple thresholding and edge detection to generate an edge map and mask.
First, we find the best location of each template in the edge map that has the minimal Chamfer matching distance, which will result in an over-completed set of leaf candidates.
Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.

In the tracking process, we develop a procedure to generate new leaves and delete small leaves.
For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
The labeled color for each leaf in the video remains the same during the tracking process.

\subsection{Performance and analysis}
The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.~.
And the {\it{SBD}} score is $0.51$ by averaging over all plants.

>>>>

\subsection{Multi-leaf segmentation and tracking framework}
We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
We treat all images in $9$ days as a video from first image on the first day to the last image in the last day. 
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates.

@@

%We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\cite{barrow1977parametric}.
Our work is motivated by Chamfer Matching technique~\cite{barrow1977parametric}, which is used to align two edge maps.
We extend it to simultaneously align multiple overlapping objects.
For plant segmentation, we use simple thresholding and edge detection to generate an edge map and mask.
The best threshold is learnt from the training set.
The edge map and mask are used in the alignment and tracking optimization.

First, we find the best location of each template in the edge map that has the minimal Chamfer matching distance, which will result in an over-completed set of leaf candidates.
Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.

In the tracking process, we delete a leaf when it becomes too small. 
We develop a procedure to generate new leaves when there is a relatively large portion of the mask has not been covered by current leaf candidates.
For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
The labeled color for each leaf in the video remains the same during the tracking process.

\subsection{Performance and analysis}
We apply our algorithm on all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
Leaf alignment is applied to the last frame of each video. 
Figure~\ref{fig:alignResult} shows some examples of leaf alignment results. 
Our framework works very well on segmenting large leaves with no overlap to neighbor leaves. 
For overlapping leaves, it becomes more challenging as the edges between the overlapping area are more difficult to be detected. 
However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(3)$ of Fig.~\ref{fig:alignResult}. 
When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(1), (4), (5)$ of Fig.~\ref{fig:alignResult}.

Leaf alignment provides the leaf candidates for tracking over time. 
One example of leaf tracking result is shown in Fig.~\ref{fig:trackExample}.

\begin{figure*}
\begin{centering}
\begin{tabular}{c c c c c c}
%\begin{tabular}{lllllllll}
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/9_1}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/10_1}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/11_1}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/12_1}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/14_1}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/15_1}\\

\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/9_2}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/10_2}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/11_2}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/12_2}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/14_2}&
\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/15_2}\\
(1) & (2) & (3) & (4) & (5) & (6) \\
\end{tabular}
\caption{Leaf alignment results on the last frame of $6$ plant videos. First row shows the original image. Second row shows the alignment result. }
\label{fig:alignResult}
\end{centering}
\end{figure*}

\begin{figure*}
\begin{centering}
\begin{tabular}{@{}c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
%\begin{tabular}{lllllllll}
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_1}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_2}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_3}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_4}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_5}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_6}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_7}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_8}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/1_9}\\

\includegraphics[width=.11\textwidth]{Figures/trackExample/2_1}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/2_2}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/2_3}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/2_4}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/2_5}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/2_6}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/2_7}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/2_8}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/2_9}\\

\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}\\

Day 1 & Day 2 & Day 3 & Day 4 & Day 5 & Day 6 & Day 7 & Day 8 & Day 9 \\
\end{tabular}
\caption{Tracking result for one video with one frame for each day.}
\label{fig:trackExample}
\end{centering}
\end{figure*}

The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.~.
And the {\it{SBD}} score is $0.59$ by averaging over all plants.

### 2015-04-29 datapapr_labeling.tex
xm's first edits
performance

\section{Annotation, Files and Protocol}

\subsection{Data statistics}
MSU-PID includes two subsets, one for each plant type: Arabidopsis and Bean.
The statistic information of these two subsets are summarised in Table~\ref{tab:stat}.
The images were acquired every hour.
As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing in the night.
In order to make sure that all four modalities present at each imaging opportunity, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.

The two subsets differs in plant image resolutions.
As shown in Figure~\ref{fig:rawIm},  we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
Therefore, the resolution of a Arabidopsis plant is much lower than that of a bean plant.
We manually crop $16$ Arabidopsis plants, which have been captured by all four sensors simultaneously.
Table~\ref{tab:resolution} summaries the image resolution of each plant in all four modalities.

@@

%\begin{figure}[h]
%\centering
%\includegraphics[width=.98\textwidth]{Figures/labelExamples}\\
%\caption{Leaf label results for one Arabidopsis plant over nine days with one image per day. }
%\label{fig:LabelExample}
%\end{figure}

@@

We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
More details can be find in~\cite{};
We define a threshold $\tau$ to operate on the corresponding tip-based errors.
By varying $\tau$, we compute the first three metrics as follows:
\begin{itemize}
  \item {\it{Unmatched Leaf Rate (ULR)}}, the percentage of unmatched leaves with respect to the total number of labeled leaves. 
This can attribute to two sources. 
The first is miss detections and false alarms. 
The second is matched leaves with tip-based errors larger than $\tau$.
  \item {\it{Landmark Error (LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
  \item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
\end{itemize}

>>>>

\section{Annotation, Files and Protocol}
\subsection{Data statistics}
MSU-PID includes two subsets, one for each plant type: Arabidopsis and Bean.
The statistic information of these two subsets are summarised in Table~\ref{tab:stat}.
The images were acquired every hour.
As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing in the night.
In order to make sure that all four modalities present at each imaging opportunity, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.

The two subsets differs in plant image resolutions.
As shown in Figure~\ref{fig:fourmodality},  we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
Therefore, the resolution of a Arabidopsis plant is much lower than that of a bean plant.
We manually crop $16$ Arabidopsis plants, which have been captured by all four sensors simultaneously.
Table~\ref{tab:resolution} summaries the image resolution of each plant in all four modalities.

@@

@@

We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
More details can be find in~\cite{yin2014b}.
We define a threshold $\tau$ to operate on the corresponding tip-based errors.
By varying $\tau$, we compute the first three metrics as follows:
\begin{itemize}
  \item {\it{Unmatched Leaf Rate (ULR)}}, the percentage of unmatched leaves with respect to the total number of labeled leaves.
This can attribute to two sources.
The first is miss detections and false alarms.
The second is matched leaves with tip-based errors larger than $\tau$.
  \item {\it{Landmark Error (LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
  \item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
\end{itemize}
